\begin{abstract}
Moltres is a multiphysics application for modeling strongly coupled neutronics
and thermal-hydraulics in liquid-fueled molten salt reactors (MSR). This paper
verifies Moltres' multiphysics MSR modeling capabilities by presenting
results from Moltres in the context of the CNRS benchmark, a
multiphysics numerical benchmark for software dedicated to modeling
fast-spectrum MSRs. The benchmark involves several steady-state and transient
subproblems of modeling
neutronics and thermal-hydraulics in a square cavity filled with U$^{233}$-based
molten salt fuel. The results show that Moltres is consistent with the other
software packages published with the CNRS benchmark. The average percentage
discrepancies calculated from the various physical parameters such as
temperature and fission rate density are mostly on the same order of magnitude
as the benchmark average. The temperature distribution shows minor deviations
due to discontinuous velocity boundary conditions on the top-left corner of the
lid-driven cavity flow. However, these deviations are limited to the boundary
values along the top of the domain and they do not noticeably impact the
overall results. As expected, Moltres agrees closest to the coupled multiphysics
package consisting of PHANTOM-$S_N$ and DGFlows from the Delft University of
Technology given the similiarities in the implementations of the neutronics,
meshing scheme, and the numerical methods for solving the multiphysics
differential equations.
\end{abstract}
